---
title: "Introduction"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache.lazy = FALSE
)
```

This short demonstration introduces some elementary capabilities of the R package [`opendiscouRse`](https://github.com/open-discourse/opendiscouRse).

```{r setup, message=F, warning=F}
library(opendiscouRse)
```

# Database setup

For the integrated __Open Discourse__ database setup to work, you must set up database the database locally, e.g. by using Docker, as [described here](https://github.com/open-discourse/open-discourse#docker-setup).

After configuring the database setup, we can obtain individual data tables from the `R6` class. In the following, we select the `politicians` table.

```{r, cache=T, eval=F}
od_obj <- OData$new()
politicians <- od_obj$get_table_data("politicians")$data
```

```{r, echo=F, results='hide', message=F, warning=F}
politicians <- readr::read_csv(here::here("tests/testthat/data/politicians.csv"))
factions <- readr::read_csv(here::here("tests/testthat/data/factions.csv"))
```


# Usage of functions

## `count` functions

### `count_data()`

For simple data aggregations, we can use `count_data()` to descriptively analyze the database. As we can see, the majority of distinct politicians holding speeches in the Bundestag are men.

```{r}
politicians |> 
  count_data(grouping_vars = "gender")
```

\

## `get` functions

### `get_age()`

Let's move to generating new columns!

With the `get_age()` function, we can easily calculate the age of politicians.

```{r}
politicians |> 
  dplyr::mutate(
    age = ifelse(
      is.na(death_date),
      # Alive politicians
      get_age(birth_date, round_val = 0),
      # Dead politicians
      get_age_hist(death_date, birth_date, round_val = 0)
    )
  ) |> 
  dplyr::select(first_name, last_name, age) |>  
  dplyr::slice(1:10)
```

For substantive analyses, the type of profession is also interesting. `get_profession_groups()` takes a `data.frame` with information regarding the professional occupation, indicated in the `politicians` data table, and returns a `data.frame` with dummy variables indicating the profession per group (we defined 7 profession categories).

```{r}
get_profession_groups(politicians, "profession") |> 
  dplyr::select(first_name, last_name, dplyr::starts_with("group_")) |> 
  dplyr::slice(1:10) 
```

<!-- Additional parliamentary information is particularly interesting for users of the __Open Discourse__ database. The number of covered electoral terms can be obtained with `get_ets()`. If we are for instance interested in how many electoral terms famous politicians, e.g. _Angela Merkel_, have covered, we can compute it easily.  -->

<!-- 8 electoral terms, what a parliamentary career! -->

<!-- ```{r} -->
<!-- speeches |>  -->
<!--   dplyr::filter(first_name == "Angela" & last_name == "Merkel") |>  -->
<!--   dplyr::mutate(electoral_term = as.numeric(electoral_term)) |>  -->
<!--   get_ets("electoral_term", merge = FALSE) -->
<!-- ``` -->

\

When investigating the background of politicians, the affiliated state (*Bundesland*) is politically of interest. State affiliations get be obtained with `get_state()`.

```{r}
get_state(
  as.numeric(politicians$id), 
  electoral_term = c(12, 17)
) |> 
  table()
```

\

For data visualization purposes (in party research), it is often desired or at least advised to use colors that match parties (or factions). `get_faction_color()` takes care fo that and yields hex color codes that can be used to visualize parties accordingly.

For that, we need to get a distinctive indication of political groups acting in the Bundestag. Let's load the `factions` table.

```{r, cache=T, eval=F}
od_obj <- OData$new()
factions <- od_obj$get_table_data("factions")$data
```

```{r}
get_faction_color(factions$abbreviation, id_type = "faction_name")
```

<!-- Ultimately, for research purposes, reporting up-to-date descriptive statistics is crucial. In articles, these are mostly reported in a _Table 1_ (also in [__Open Discourse__'s data paper](https://osf.io/preprints/socarxiv/dx87u/). `get_table_1()` takes care of that and generates an up-to-date _Table 1_. -->

<!-- ```{r, cache=T} -->
<!-- table_1 <- get_table_1( -->
<!--   speeches, -->
<!--   contributions_simplified -->
<!-- ) -->

<!-- table_1 |>  -->
<!--   kableExtra::kbl(caption = "Descriptive Statistics of Speeches and Contributions") |>  -->
<!--   kableExtra::kable_classic(full_width = F) -->
<!-- ``` -->

\

## `plot` functions

### `plot_cov()`

The package comes with several plotting functions. For descriptive purposes, we might be interested in the coverage of the data table. `plot_cov()` visualizes `NAs` for the whole table. Of course, there is a `ggplot2` __Open Discourse__ theme.

```{r}
plot_cov(politicians) +
  theme_od()
```

\

### `plot_count()`

As shown above, `count_data()` computes counts per grouping variables. `plot_count()` builds on that and is able to visualize this type of counted data specifically. If we also incorporate the Bundesland (state) affiliation through `get_state()`, we can show how the distribution of gender across states looks like.

```{r}
politicians |> 
  dplyr::mutate(state = get_state(id, electoral_term = 19)) |> 
  dplyr::filter(!is.na(state)) |> 
  count_data(grouping_vars = c("state", "gender")) |>
  plot_count(x_var = "gender", facet_var = "state") +
  theme_od() + 
  ggplot2::ggtitle("Gender of Parliamentary Speakers by State in the 19. Bundestag")
```

